---
title: "frank_wang_homework4"
author: "Nathan Frank and Yen Wang"
date: "2/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Team members: Yen Wang, Nathan Frank

link to github repo: https://github.com/natefrank48/lab2

### What is the overall number of chocolate bars rated? How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
choco = read.csv("choco.csv")
print(nrow(choco))
```
```{r}
ggplot(data = choco, aes(x = Review.Date)) + geom_bar() + 
  xlab("Year") + 
  ylab("Number of Ratings") + 
  ggtitle("Number of Ratings Each Year")
```


### How are ratings distributed?
```{r}
ggplot(data = choco, aes(x = Rating)) + 
  geom_histogram(bins = 33) + 
  ggtitle("Distribution of the Ratings")
```

From the histogram above, we can see that most of the chocolate has a rating between 2.3 and 4. More than 400 chocolate rated has a rating of 3.5 where only one chocolate got above 4.0 and a less than 20 got below a 2.0

### Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(data = choco, aes(x = Rating, y = Cocoa.Pct)) + 
  geom_point() + 
  ggtitle("Cocoa Percentage vs Rating")
```
From the scatter plot above, we can conclude that the ratings do not depend on the coca percentage of a chocolate bar. Since the cocoa percentage of most chocolate is between 60 and 85 and the outliers' ratings are also in that range. 





